|

### 2020-06-30 paper.Rmd
Implementation rewritten.

## Parametrised rescaling

@@

Note that for the purpose of fitting the displayed data onto a pre-defined display (e.g. range $[-1,1]$), we can directly scale $r'$, e.g. by a factor $x/R$ where $x$ sets the range on the display, e.g. $x=0.9$ in what follows. We then calculate the new plotting coordinates $x', y'$ from $r', \theta$.

>>>>

## Parametrised rescaling {#sec:params}

@@

The sage display has been implemented in R [@rref] in the `display_slice` method in the `tourr` package [@tourr]. This display has two important new input parameters, the scaling `s` for computing $p_{eff}$, and the overall scale `R`. Both these parameters are described in Section \ref{sec:params} above.

Note that the ratio of the `tourr` parameter `half_range` and the new parameter `R` set the scale for fitting the displayed data on the plotting canvas ranging between $[-1,1]$. With the default settings `half_range` = `R` and we apply a scaling factor $0.9$ to contain the projected points within the display.

Below we show example code demonstrates how the new display redistributes the projected points drawn uniformly inside a 5D hypersphere.
```{r codeExampel, echo=TRUE, eval=FALSE}
library(tourr)
# use geozoo to uniformly generate points inside a 5D sphere
sphere5 <- geozoo::sphere.solid.random(5)$points
colnames(sphere5) <- c("x1", "x2", "x3", "x4", "x5") # naming variables
# standard tour animation with default settings
animate_xy(sphere5)
# new sage display to redistribute the points based on projected volume
animate_sage(sphere5)
# we can use R and s to tune the display
# for example use R to zoom in near the center
# we also adjust half_range to fit the display on the plotting canvas
animate_sage(sphere5, R = 0.1, half_range = 0.1)
```
